\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2016-04-07 paper/paper.tex
minor fix in discussion
abstract

\noindent This will be the abstract of the paper

@@

\subsection{Comparison}

>>>>

\noindent The worst-case asymptotic time complexity for a basic and fast color refinement algorithm are calculated to be $O(N^3)$ and $O(M\cdot{}log(N)$ respectively. Computational results for a three paths type graph indicate different time complexities, at least for that specific type of graph. It can be concluded that either the algorithms are faster for the three paths graphs, or the calculations for the time complexity are incorrect.

@@
